
\section{Formal Verification}

In order to make sure that the security properties of Disco retain the security properties of the Noise protocol frameworks, formal analysis can be helpful. In this section we detail preliminary work done with the Tamarin Prover tool\cite{tamarinProver} in order to model the IK handshake of Disco.

Tamarin Prover is a security protocol verification tool that supports both falsification and unbounded verification in the symbolic model. Thanks to built-ins for diffie-hellman and the XOR operation, most of the operations of Disco except for Strobe can easily be modeled. In order to model Strobe calls, we need to model the underlying duplex construction. We note that the security of the duplex construction is equivalent to the one of the sponge construction (as seen in lemma 3 of \cite{spongeduplex}), and that a keyed sponge construction can be modeled as a random oracle\cite{keyedsponge}. For this reason, we model each calls to Strobe as a single call to a random oracle function in Tamarin Prover: \mintinline{python}{functions: sponge\1}. For example, we model a call to \mintinline{python}{send_ENC()} followed by a call to \mintinline{python}{send_MAC} as:

\begin{minted}[breaklines,frame=single,linenos]{python}
input2 = <'ENC', input1>
ciphertext = sponge(input2) ⊕ plaintext
input3 = <plaintext, input2>
input4 = <'MAC', input3>
tag = sponge(input4)
input5 = <'0000000000000000', input4>
\end{minted}

* the reverse pairs is used because of Tamarin ways to handle pairs
* the sponge call on line 5 is equivalent to \mintinline{python}{sponge(<'MAC', plaintext, 'ENC', input1>)}

\textbf{Strobe specific}:

* a permutation in strobe is required, usually before using the state directly to encrypt or produce something that MUST be based on what was absorbed previously. Permutating force absorption to matter.
* we take care of this by calling \mintinline{python}{sponge()} when we need it
* 'MAC' and 'ENC' are also markers that are abstractions of what happen later. We do not care about 'send_' or 'recv_' are these are implementation specific concerns

\textbf{Tamarin specific}:

* built-ins: diffie-hellman, xor
* allow us to do mostly everything
* what to prove?
* 7.7. Payload security properties
* 7.8. Identity hiding
* of noise specification. Contains things like KCI, authentication, replays at every point of the protocol, and from each point of view
